Variational Monte Carlo on bosonic systems

### 2018-04-03 project_1/article/article.tex
Add table and plot of one-body densities

        \subsubsection{Finding the minimum}
            Using the method of gradient descent we choose a set of six starting
            $\alpha_0 \in [0.2, 0.8]$ and try to locate a value for $\alpha$
            where the gradient goes to zero. We looked at $N = 10$ with $d = 3$,
            $\omega = 1$ and $\beta = \lambda = \sqrt{8}$. This yields the value
            for the minimum $\alpha$ to be
            \begin{align}
                \alpha = 0.49744 \pm 0.00002.
            \end{align}
            In \autoref{fig:gradient_descent_interacting} we can see how the
            conjugate gradient method ``moves'' to find the optimal value of
            $\alpha$.

@@

		\subsubsection{One-Body Densities}

>>>>

        \subsubsection{Finding the minimum}
            Using the method of gradient descent we choose a set of six starting
            $\alpha_0 \in [0.2, 0.8]$ and try to locate a value for $\alpha$
            where the gradient goes to zero. We looked at $N = 10$ with $d = 3$,
            $\omega = 1$ and $\beta = \lambda = \sqrt{8}$. This yields the value
            for the minimum $\alpha$ to be
            \begin{align}
                \alpha = 0.49744 \pm 0.00002.
                \label{eq:optimal_interacting_alpha}
            \end{align}
            In \autoref{fig:gradient_descent_interacting} we can see how the
            conjugate gradient method ``moves'' to find the optimal value of
            $\alpha$.

@@

        \subsubsection{One-Body Densities}
            We now look at one-body densities for the value of $\alpha$ found in
            \autoref{eq:optimal_interacting_alpha}.

            \begin{table}
                \caption{Comparison of the elliptical system with an elliptical
                gaussian trial wavefunction with and without the Jastrow
                factor.}
                \centering
                \begin{ruledtabular}
                    \begin{tabular}{r|rr|rr}
                        & \multicolumn{2}{c|}{Interacting}
                        & \multicolumn{2}{c}{Non-interacting} \\
                        \hline
                        $N$ & $\expval{E}$ & $\sigma_b$ & $\expval{E}$
                        & $\sigma_b$ \\
                        \hline
                        10 & 24.3986 & 0.0003 & 24.1418 & 0.0002 \\
                        50 & 127.2852 & 0.0077 & 120.7129 & 0.0012 \\
                        100 & 266.2904 & 0.0297 & 241.4248 & 0.0025
                    \end{tabular}
                \end{ruledtabular}
                \label{tab:10_optimal}
            \end{table}

            \begin{figure}
                \includegraphics[width=244px]
                {../data/figures/problem_g_100N.pdf}
                \caption{In this figure the interacting and non-interacting
                densities correspond to the elliptical potential with and
                without the Jastrow factor respectively. The ``ideal'' system is
                the spherical potential with the non-interacting Gaussian trial
                wavefunction.}
                \label{fig:one_body_density_100}
            \end{figure}
